---
title: "Intro_DS_HW2"
output: html_document
---

## Problem 1: Fizz Buzz

```{r, echo=F}
for (i in 1:1000){
if ((i %% 3 != 0) & (i %% 5 != 0) )  {print(i)}
  else if ((i %% 3 == 0) & (i %% 5 == 0)) {print("Fizz Buzz")}
  else if (i %% 3 == 0) {print("Fizz")}
  else if (i %% 5 == 0) {print("Buzz")}
  else print(i)
}
```

## Problem 2 : Map 

``` {r}

Teams = c("Real Madrid", "FC Barcelona", "Atlético Madrid", "Athletic Bilbao", "Valencia")   
City = c("Madrid", "Barcelona", "Madrid", "Bilbao", "Valencia")
Champions = c(33, 25, 10, 8, 6)
lon = c(-3.7037902, 2.1734035, -3.7037902, -3.7037902, -0.3762881)
lat = c(40.41678, 41.38506, 40.41678, 43.26301, 39.46991)

City_coord = data.frame(cbind(lon,lat))
City_coord$Champions <- Champions
City_coord$Teams <- Teams
City_coord$City <- City

City_coord

library(htmltools)
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%
  addCircleMarkers(lng=City_coord$lon, lat=City_coord$lat,
                   radius = City_coord$Champions*1.5) %>%
  addPopups(-3.7037902, 40.41678, paste(sep = "<br/>",
                                        "<b> Real Madrid </b>",
                                        33,
                                        "<b> Atlético Madrid</b>",
                                        10),
            options = popupOptions(closeButton = FALSE)) %>% 
  addPopups(2.1734035, 41.38506, paste(sep = "<br/>",
                                        "<b> FC Barcelona </b>",
                                        25),
            options = popupOptions(closeButton = FALSE)) %>%
  addPopups(-3.7037902, 43.26301, paste(sep = "<br/>",
                                       "<b> Athletic Bilbao </b>",
                                       8),
            options = popupOptions(closeButton = FALSE)) %>% 
  addPopups(-0.3762881, 39.46991, paste(sep = "<br/>",
                                        "<b> Valencia </b>",
                                        6),
            options = popupOptions(closeButton = FALSE))
  
m
